data_cleaning

### 2015-11-19 analysis/exp_data_clean.Rmd
updated file path in exp_data_clean.Rmd for e6 and e11 for correct column labeling

# If set to TRUE then enroce compliance for e8 (n reduced to 16)
if (FALSE) { # Enforce compliance check for training 1
  d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1", 
         compliant == TRUE)
} else { # Only enforce language check
  d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1")
}

@@

# Output to CSV
# --------------
#write.csv(ms, "../models/L1_e6.csv", row.names=FALSE)
```

@@

## Cleaning / formatting - output
```{r}
# Preliminary data cleaning
# -------------------------
ms <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(listener.p = n() / n[1])
# Output to CSV
# --------------
#write.csv(ms, "../models/L1_e11.csv", row.names=FALSE)
```

>>>>

# If set to TRUE then enforce compliance for e8 (n reduced to 16)
if (FALSE) { # Enforce compliance check for training 1
  d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1", 
         compliant == TRUE)
} else { # Only enforce language check
  d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1")
}

@@

# Output to CSV
# --------------
# write.csv(ms, "../models/model_data/L1_e6.csv", row.names=FALSE)
```

@@

## Cleaning / formatting - output
```{r}
# Preliminary data cleaning
# -------------------------
ms <- d %>%
  group_by(degree, scale) %>%
  mutate(n = n()) %>%
  group_by(degree, scale, stars) %>%
  summarise(listener.p = n() / n[1])
# Output to CSV
# --------------
write.csv(ms, "../models/model_data/L1_e11.csv", row.names=FALSE)
```
